Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-09-20 manuscript/manuscript.tex
incrementing figure numbers
adding new figure 1 (HMM scheme)

@@

\begin{figure}
\includegraphics[width=0.48\textwidth]{figure_1}
\caption{The PyEMMA workflow: MD trajectories are processed and discretized (first row).
A Markov state model is estimated from the resulting discrete trajectories and validated (middle row).
By iterating between data processing and MSM estimation/validation,
a dynamical model is obtained that can be analyzed (last row).}
\label{fig:workflowchart}
\end{figure}

@@

\begin{figure}
\includegraphics{figure_2}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone:
(a)~The Trp-Leu-Ala-Leu-Leu pentapeptide in licorice representation~\cite{vmd}.
(b)~The VAMP-2 score indicates which of the tested featurizations contains the highest kinetic variance.
(c)~The sample free energy projected onto the first two time-lagged independent components (ICs) at lag time $\tau=0.5$~ns shows multiple minima and
(d)~the time series of the first two ICs of the first trajectory show rare jumps.}
\label{fig:io-to-tica}
\end{figure}

@@

\begin{figure}
\includegraphics{figure_3}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone:
(a)~The convergence behavior of the implied timescales associated with the four slowest processes.
(b)~Chapman-Kolmogorov test computed using an MSM estimated with lag time $\tau=0.5$~ns assuming~5 metastable states.
The solid lines in (a) refer to the maximum likelihood result while the dashed lines show the ensemble mean computed with a Bayesian sampling procedure~\cite{ben-rev-msm}.
The black line indicates where implied timescales are equal to the lag time,
whereas the grey area indicates all implied timescales faster than the lag time.
In both panels, the (non-grey) shaded areas indicate~$95\%$ confidence intervals computed with the aforementioned Bayesian sampling procedure.}
\label{fig:its-and-ck}
\end{figure}

@@

\begin{figure}
\includegraphics{figure_4}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone:
(a)~The reweighted free energy surface projected onto the first two independent components exhibits five minima which
(b)~PCCA++ identifies as five metastable states.
(c)~The second right eigenvector shows that the slowest process shifts probability between the least probable state ($\mathcal{S}_1$) and the other states,
in particular states ($\mathcal{S}_4$, $\mathcal{S}_5$), whereas
(d)~the committor $\mathcal{S}_2\to\mathcal{S}_4$ indicates that states $\mathcal{S}_{(1,3,5)}$ act as a transition region between states $\mathcal{S}_2$ and $\mathcal{S}_4$.}
\label{fig:msm-analysis}
\end{figure}

@@

\begin{figure}
\includegraphics{figure_5}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone:
visualization of the transition paths from $\mathcal{S}_2$ to $\mathcal{S}_4$.
Metastable states $\mathcal{S}_{(1-5)}$ are represented by an ensemble of representative structures and are arranged along the horizonal axis according to their committor probabilities.
The three main transition pathways starting from $\mathcal{S}_2$ and ending in $\mathcal{S}_4$ are depicted by gray arrows with thickness proportional to the transition flux.
The dominant pathway proceeds through $\mathcal{S}_5$.}
\label{fig:tpt-network}
\end{figure}

@@

\begin{figure}
\includegraphics{figure_6}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone:
(a)~the Trp-1 SASA autocorrelation function yields a weak signal which, however,
(b)~can be enhanced if the system is prepared in the nonequilibrium condition $\mathcal{S}_1$.
The solid/orange lines denote the maximum likelihood MSM result;
the dashed/blue lines and the the shaded areas indicate sample means and~$95\%$ confidence intervals computed with a Bayesian sampling procedure~\cite{ben-rev-msm}.}
\label{fig:msm-exp-obs}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=0.48\textwidth]{figure_1}
\caption{The HMM transition matrix $\tilde{\mathbf{P}}(\tau)$ propagates the hidden state trajectory $\tilde{s}(t)$ (orange circles) and, at each time step $t$, the emission into the observable state $s(t)$ is governed by the emission probability $\bm{\chi}\left( s(t) \middle| \tilde{s}(t) \right)$.}
\label{fig:hmm-scheme}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.48\textwidth]{figure_2}
\caption{The PyEMMA workflow: MD trajectories are processed and discretized (first row).
A Markov state model is estimated from the resulting discrete trajectories and validated (middle row).
By iterating between data processing and MSM estimation/validation,
a dynamical model is obtained that can be analyzed (last row).}
\label{fig:workflowchart}
\end{figure}

@@

\begin{figure}
\includegraphics{figure_3}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone:
(a)~The Trp-Leu-Ala-Leu-Leu pentapeptide in licorice representation~\cite{vmd}.
(b)~The VAMP-2 score indicates which of the tested featurizations contains the highest kinetic variance.
(c)~The sample free energy projected onto the first two time-lagged independent components (ICs) at lag time $\tau=0.5$~ns shows multiple minima and
(d)~the time series of the first two ICs of the first trajectory show rare jumps.}
\label{fig:io-to-tica}
\end{figure}

@@

\begin{figure}
\includegraphics{figure_4}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone:
(a)~The convergence behavior of the implied timescales associated with the four slowest processes.
(b)~Chapman-Kolmogorov test computed using an MSM estimated with lag time $\tau=0.5$~ns assuming~5 metastable states.
The solid lines in (a) refer to the maximum likelihood result while the dashed lines show the ensemble mean computed with a Bayesian sampling procedure~\cite{ben-rev-msm}.
The black line indicates where implied timescales are equal to the lag time,
whereas the grey area indicates all implied timescales faster than the lag time.
In both panels, the (non-grey) shaded areas indicate~$95\%$ confidence intervals computed with the aforementioned Bayesian sampling procedure.}
\label{fig:its-and-ck}
\end{figure}

@@

\begin{figure}
\includegraphics{figure_5}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone:
(a)~The reweighted free energy surface projected onto the first two independent components exhibits five minima which
(b)~PCCA++ identifies as five metastable states.
(c)~The second right eigenvector shows that the slowest process shifts probability between the least probable state ($\mathcal{S}_1$) and the other states,
in particular states ($\mathcal{S}_4$, $\mathcal{S}_5$), whereas
(d)~the committor $\mathcal{S}_2\to\mathcal{S}_4$ indicates that states $\mathcal{S}_{(1,3,5)}$ act as a transition region between states $\mathcal{S}_2$ and $\mathcal{S}_4$.}
\label{fig:msm-analysis}
\end{figure}

@@

\begin{figure}
\includegraphics{figure_6}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone:
visualization of the transition paths from $\mathcal{S}_2$ to $\mathcal{S}_4$.
Metastable states $\mathcal{S}_{(1-5)}$ are represented by an ensemble of representative structures and are arranged along the horizonal axis according to their committor probabilities.
The three main transition pathways starting from $\mathcal{S}_2$ and ending in $\mathcal{S}_4$ are depicted by gray arrows with thickness proportional to the transition flux.
The dominant pathway proceeds through $\mathcal{S}_5$.}
\label{fig:tpt-network}
\end{figure}

@@

\begin{figure}
\includegraphics{figure_7}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone:
(a)~the Trp-1 SASA autocorrelation function yields a weak signal which, however,
(b)~can be enhanced if the system is prepared in the nonequilibrium condition $\mathcal{S}_1$.
The solid/orange lines denote the maximum likelihood MSM result;
the dashed/blue lines and the the shaded areas indicate sample means and~$95\%$ confidence intervals computed with a Bayesian sampling procedure~\cite{ben-rev-msm}.}
\label{fig:msm-exp-obs}
\end{figure}
